---
title: "Assignment 2"
author: "Vibhor Dabas"
format: html
editor: visual
---

## STEP 1 -

Created a example.qmd file in r project and setting format to html so that it can be knitted into html.

```{r}
# Hello! This is my second assignment

# Below is just a simple maths calculation
4*4


```

## STEP 2 -

1.  Firstly use git command in terminal of R studio - `pwd` this tells us where is our current working directory, it should be same where your R project is created.
2.  Initializing this folder by using git command - `git init` in terminal.
3.  Now using git command - `git status` to check local repo status.
4.  After that using git command - `git add .` to stage all changes in file present in our folder.
5.  Then, using git command - `git commit -m "Created example.qmd file"` which saves snapshot of the staged files with a descriptive message.
6.  Before next steps you must ensure that you create a repo on Github and copy ssh key
7.  Now using git command - `git remote add origin ___` and paste ssh key after origin to connect local repo to Github.
8.  After cloning repo use git command - `git branch` this helps to indicate which branch are we on.
9.  Lastly using git command - `git push -u origin main` to push changes staged previously made in .qmd file to github.

## STEP 3 -

```{r}

# This section was added in testbra

```

1.  Creating a new branch "testbranch" by using git command - `git branch testbranch`
2.  Now add a comment in a new r code chunk " This section was added in testbranch ".
3.  After adding section in R code chunks, switch to "testbranch" by using git command - `git switch testbranch`
4.  Now use 3 step work flow to commit and push the changes to remote repo which by using following git commands, firstly - `git add .`, secondly - `git commit -m "added new section in qmd file"`, and lastly `git push origin testbranch`.

## STEP 4 -

1.  Make a data folder using git command - `mkdir data`
2.  Now copy files which are present in data folder of assignment 1 and paste them into      this data folder.
3.  Now use git command - `git add data` to stage the folder.
4.  Then using git command - `git commit --amend -m "Updated qmd file  and added data folder"` to ammend the previous commit.
5.  Finally, using git command - ` git push --force origin testbranch ` to push the          changes and using "--force" which replaces the old commit wiht the updated ammended      commit from the local repo.


## STEP 5 -

1. 













